### 2014-08-01 Docs/mg/mg.tex
add a definition of bndry_reg from Ann

\subsection{\mgtower}

@@

>>>>

\subsection{Data Structures}

\subsubsection{\mgtower}

@@

\subsection{\bndryreg}

A \bndryreg\ is a set of {\tt dim*2} multifabs defined on the coarse cells
immediately outside of each fine grid.

Ideally we would only include the cells not covered by a different
fine grid, but in the current implementation, for {\tt N} fine grids we have
{\tt N*dim*2} multifabs (the factor of 2 is {\tt lo}/{\tt hi}).

We use the \bndryreg to store the correction to the residual to be
used in the coarse grid relaxation.  The way we use it is that we
compute a pure coarse grid residual in every coarse cell, then we
correct it by subtracting the contribution of the coarse flux under
the coarse-fine edge and adding the contribution of the fine fluxes at
that same interface.  The \bndryreg\ holds the cell-centered
contribution from the difference of these edge fluxes and is added to
the coarse residual multifab.
